Contracts for unions and intersections are hard for Nickel

### 2021-05-12 paper.tex
Flat contracts improvementes

\subsection*{User defined (flat) contracts}

User defined contracts, also called flat contracts, are a particular
kind of contract that behaves similar to an assertion, and whose
main point is to apply some arbitrary predicate (as arbitrary as the
host language allows it) to a value; if the predicate returns true,
the contract passes, otherwise it fails.

For instance, we could define a flat contract $even?$ as
$\lambda x. ~ x ~ \% ~ 2 ~ == ~ 0$, that checks
whether a number is even.
And then use it to check that a function always returns an
even number, for example:

$$let~f~=~(\lambda n. ~ n * 2)@Number ~ \rightarrow ~ even?$$

\unsure{Do we need deeper examples?}

This kind of contracts are present on many different languages,
for instance, the Eiffel programming language, the precursor
on the Design by Contract ideals, allows to assert
exactly these kinds of expression as pre- and post-conditions on
functions.

The Racket programming language also has a system to work with
contracts\footnote{And a gradual typing system
built on top of that, but that goes beyond the scope of this
work.} that provides a mechanism for defining them; and
composing these with other kinds of constructs.

Even if flat contracts may seem like too much, these are expected
by programmers on dynamic languages, where testing and runtime
assertions are a common pattern for safe programming, and
programmers are used to express complex predicates
over values.

>>>>

\subsection*{Flat contracts}

User defined contracts, also called flat contracts, are a particular
kind of contract that behaves similar to an assertion, and whose
main point is to apply some arbitrary predicate (as arbitrary as the
host language allows it) to a value; if the predicate evaluates to
true, the contract passes, otherwise it fails.

For instance, we could define a flat contract $even?$ as
$\lambda x. ~ x ~ \% ~ 2 ~ == ~ 0$, that checks
whether a number is even by checking the remainder of dividing it by 2.
And then use it to check that a function always returns an
even number, when applied to a $Number$:

$$let~f~=~(\lambda n. ~ n * 2)@(Number ~ \rightarrow ~ even?)$$

\unsure{Do we need deeper examples?
Maybe something showing that flat contracts could evaluate
a function.}

This kind of contracts are present on many different languages,
for instance, the Eiffel programming language, the precursor
of the Design by Contract ideals, allows to assert
these kinds of expression as pre- and post-conditions on
functions\cite{EiffelDesignByContract}.
A somewhat newer language, the D programming
language, allows, among other things, to have invariants on classes,
written with flat contracts\cite{DLangContracts}.

Finally, the Racket programming language also has a system to work with
contracts\footnote{And a gradual typing system
built on top of that, but that goes beyond the scope of this
work.} that allows to define flat contracts, and
to compose them with other kinds of dynamic checks,
like higher order contracts or a lightweight take on union
and intersection contracts\cite{RacketContracts}.
\todo{Talk about this, probably later on the paper}

Even if flat contracts may seem like too much, the ability to make
non trivial checks on values (to validate their output) is expected
by programmers on dynamic languages, where testing and runtime
assertions are a common pattern for safe programming, and
programmers are used to express complex predicates
over values.
